Named Entity Recognition as Structured Prediction

### 2012-11-11 doc/report/paper.tex
Minor changes, experiment.

\exg. \textbf{x:} The motor company ' Ford ' was founded and incorporated by Henry Ford .\\
      \textbf{y:}  O   O      O     0 ORG  O  O     O     O       O        O PER   PER  O  \label{PredEx1b} \\
\caption{Input and predicted structure for the Named Entity Recognition task.}

@@

As the predicted structure, we use the labels for every token in the full sentence. If a token is not a \namedentity, it is assigned the label \Oo.

Learning is implemented using the Structured Perceptron algorithm. To avoid overfitting, we average the parameters after the last iteration \cite{collins2002discriminative}. 
For finding the best sequence of labels for a sentence, we use a modified version of the Viterbi algorithm. The algorithm finds the sequence $\hat{y}$, such that:

\[
\hat{y} = \argmax_{\mathbf{y} \in \mathcal{Y}^{n}} \sum_{i=1}^{n}\mathbf{w} \cdot \boldsymbol{f}(\mathbf{x}, i, y_{i-1}, y_{i})
\]

This sequence can be computed efficiently in $ O( N^2 |\mathbf{x}| ) $ via dynamic programming. 
As a first step, the trellis has to be constructed, then we have to find the $ a \in \mathcal{Y}$ in the 
last column of the trellis with maximal score $\delta_n(a)$. From this, the sequence can be recovered via back-tracking trough the trellis. 
The score of the best sequence ending in $a$ is:

\[
\delta_i(a) = \max_{\mathbf{y} \in \mathcal{Y}^{n}, y_n = a} \sum_{j=1}^{n}{\mathbf{w} \cdot \boldsymbol{f}(\mathbf{x}, j, y_{j-1}, y_{j})}
\]

@@

One of the issues that we needed to address is the case of headlines. Headlines, mainly in the English data, are often written entirely in uppercase letters. This is problematic because from most of the data, the model might learn that a word in all uppercase letters is indicative of an organization (e.g.\ IBM, AIG, NYSE) and might thus mistake the tokens in headlines for organizations. We address this issue by converting all-uppercase headlines into their most likely original case (truecasing). To estimate the most likely case of a token from a monolingual corpus, we use the truecasing model from the Moses statistical machine translation system \cite{koehn2007moses}.

@@

@@

This paper presented a system for \namedentity Recognition using Structured Prediction.

>>>>

\exg. \textbf{x:} The motor company ' Ford ' was founded and incorporated by Henry Ford .\\
      \textbf{y:}  O   O      O     0 ORG  O  O     O     O       O        O PER   PER  O  \label{PredEx1b} \\

\caption{Input and predicted structure for the Named Entity Recognition task.}
%\label{fig:predxy}

@@

As the predicted structure, we use the labels for every token in the full sentence (see Figure~3). If a token is not a \namedentity, it is assigned the label \Oo.

Learning is implemented using the Structured Perceptron algorithm. To avoid overfitting, we average the parameters after the last iteration \cite{collins2002discriminative}. 
For finding the best sequence of labels for a sentence, we use a modified version of the Viterbi algorithm. The algorithm finds the sequence $\hat{y}$, such that:
\[
\hat{y} = \argmax_{\mathbf{y} \in \mathcal{Y}^{n}} \sum_{i=1}^{n}\mathbf{w} \cdot \boldsymbol{f}(\mathbf{x}, i, y_{i-1}, y_{i})
\]

This sequence can be computed efficiently in $ O( N^2 |\mathbf{x}| ) $ via dynamic programming. 
As a first step, the trellis has to be constructed, then we have to find the $ a \in \mathcal{Y}$ in the 
last column of the trellis with maximal score $\delta_n(a)$. From this, the sequence can be recovered via back-tracking trough the trellis. 
The score of the best sequence ending in $a$ is:
\[
\delta_i(a) = \max_{\mathbf{y} \in \mathcal{Y}^{n}, y_n = a} \sum_{j=1}^{n}{\mathbf{w} \cdot \boldsymbol{f}(\mathbf{x}, j, y_{j-1}, y_{j})}
\]

@@

One of the issues that we needed to address is the case of headlines. Headlines, mainly in the English data, are often written entirely in uppercase letters. This is problematic because from the data, the model might learn that a word in all uppercase letters is indicative of an organization (e.g.\ IBM, AIG, NYSE) and might thus mistake the tokens in headlines for organizations. We address this issue by converting all-uppercase headlines into their most likely original case (truecasing). To estimate the most likely case of a token from a monolingual corpus, we use the truecasing model from the Moses statistical machine translation system \cite{koehn2007moses}.

@@

The experiment above has shown that the gazetteer features are beneficial for Dutch. In this experiment, we want to explore whether the gazetteer features can be improved by extending the monolingual gazetteer with entries from other languages. For this, we compare the Dutch-only gazetteer with a gazetteer extended with English data.

@@

In this paper, we presented a \namedentity~Recognition system based on the concept of Structured Prediction. While the system does not achieve state-of-the-art performance on the CoNLL shared task, we believe that the results are res
